Estimation of Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra with the Hydrogen Epoch of Reionization Array

### 2015-12-09 DishReflectometry/Paper1_v0.tex
Minor formatting changes,

\documentclass[12pt,preprint]{aastex}
\usepackage{float,amsmath}
%\usepackage[margin=1in]{geometry}
%\usepackage{titlesec} %used to format titles
\usepackage{graphicx} %for handling figures
%\usepackage[none]{hyphenat} %disallows hyphenated words
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\volt}{{v}}
\newcommand{\vis}{{V}}
\newcommand{\sky}{{\rm sky}}
\newcommand{\bmvolt}{{a}}
\newcommand{\bm}{{A}}
\newcommand{\thhat}{{\hat\theta}}
\newcommand{\fngexp}{{e^{\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
\newcommand{\ifngexp}{{e^{-\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
\newcommand{\dfngexp}{{e^{2\pi i\nu \Delta \tau}}}
\newcommand{\myemail}{skywalker@galaxy.far.far.away}

@@

\begin{figure}[ht!]
\centering
\includegraphics[trim={2cm 20cm 30cm 15cm},clip, totalheight=0.3\textheight]{plots/heradish.jpg}
\caption{HERA dish and feed at the Green Bank NRAO site.}
\label{fig:heradish}
\end{figure}

@@

\subsection{Delay spectrum: An estimate of the 21cm power spectrum}
Add text here. 
 \textbf{[ Reference to Nithya's foreground simulation work, reference to any plots on the relative contribution of the  foreground and EoR signal. ]}

@@

%need to add in third : Antenna feed focal length 4.5 m which corresponds to a
%signal propagation delay of 0.3 ns. Hence, subsequent reflections from the dish
%vertex are expected to be at a delay which is integral multiple of 0.3 nS.
\begin{figure}[ht!]
\centering
\includegraphics[totalheight=0.4\textheight]{plots/frequency_amp_phase_fullbw.png}
\caption{Amplitude and phase of the measured return loss. Colored dashed lines
mark three different frequency bands: $140-160MHz$ (typical power spectrum bandwidth), $100-200MHz$ (PAPER bandwidth), and
$50-250MHz$ (HERA bandwidth).}
\label{fig:freq}
\end{figure}
%++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

\begin{figure}
\centering
\includegraphics[width=1.0\linewidth]{plots1/delayspectrum.png}
\caption{Delay transform of the transfer function of the HERA element. The complex return loss of the element is measured between 50 to 400~MHz when the feed is kept at the focal plane of the dish at a focal height 4.5m. The delay spectrum is produced by taking the Fourier transform of the magnitude of the return loss measurement after limiting the measurements between 100 to 200~MHzusing Blackman-Harris window. The intersection of the horizontal and vertical dashed line shows the instrument performance specification as predicted by the theory of delay transform in order to detect the 21cm power spectrum.}
\label{fig:window}
\end{figure}

\begin{figure}
\centering
\includegraphics[totalheight=0.6\linewidth]{plots1/delayspectrum_feed.png}
\caption{Delay transform of the transfer function of the HERA feed element. The feed is kept on the ground downside up so that the entire radiation from the feed is radiated out. Once again, the measurement is done between 50 to 450 MHz and the delay spectrum is produced between $100-200$~MHz by using a Blackman-Harris window. The black dashed lines illustrate the instrument specification.}
\label{fig:outofthedish}
\end{figure}

@@

The delay response of the instrument is dependent on the band chosen for the Fourier transform.
%As one might expect, in regions where the feed return loss is low, reflections are minimized.  Thus, we cannot ignore that these measurements were performed
%using a PAPER-style feed tuned for efficient operation over a $100-200MHz$ bandwidth. 
The measurement bandwidth effects the amplitude and phase of the delay spectrum. Fourier transforms taken over wider bandwidth
become dominated by the feed sidelobes outside the operating band, making the resultant delay profiles less relevant
for the power spectrum performance of the HERA instrument.  Conversely, when performing Fourier transforms over much 
narrow bands (the windowed $20MHz$ bands typical of PAPER analysis), the width of the resulting delay profile
becomes dominated by sidelobes of low delay emission interacting with the narrow bandwidth kernel.  
Although this may appear to be a relevant performance metric for PAPER power spectrum analysis, such an analysis typically pre-filters out low-delay emission using wide bandwidths precisely to avoid sidelobes from low-delay emission.  Hence, the most relevant delay-spectrum performance profile is that taken using the $100-200MHz$ band. \textbf{In the $100-200MHz$ delay profile, we see a delay response of $-25dB$ at $60ns$, which slopes down to $-60dB$ at $\sim120ns$.  WRITE AGAIN}
\begin{figure}[ht!]
\centering
\includegraphics[width=1.0\linewidth]{plots1/delayspectrum_height.png}
\caption{Delay transform of the transfer function of the HERA element keeping the feed at various heights. Delay transform is produced by taking the Fourier transform of the measurement using Blackman-Harris window.}
\label{fig:elevator}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[totalheight=0.41\textheight]{plots/delay_feed.png}
\caption{Delay plots produced using a Hamming window function for different feed only configurations and the PAPER bandwidth ($100MHz-200MHz$). The black dashed lines illustrate our ``60 by 60" specification.}
\label{fig:outofthedish}
\end{figure}

>>>>

%\documentclass[12pt,preprint]{aastex}
\documentclass[iop]{emulateapj}
\usepackage{float,amsmath}
%\usepackage[margin=1in]{geometry}
%\usepackage{titlesec} %used to format titles
\usepackage{graphicx} %for handling figures
%\usepackage[none]{hyphenat} %disallows hyphenated words
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\volt}{{v}}
\newcommand{\vis}{{V}}
\newcommand{\sky}{{\rm sky}}
\newcommand{\bmvolt}{{a}}
%\newcommand{\bm}{{A}}
\newcommand{\thhat}{{\hat\theta}}
\newcommand{\fngexp}{{e^{\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
\newcommand{\ifngexp}{{e^{-\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
\newcommand{\dfngexp}{{e^{2\pi i\nu \Delta \tau}}}
\newcommand{\myemail}{skywalker@galaxy.far.far.away}

@@

\begin{figure*}
\centering
\includegraphics[trim={2cm 20cm 30cm 15cm},clip, totalheight=0.3\textheight]{plots/heradish.jpg}
\caption{HERA dish and feed at the Green Bank NRAO site.}
\label{fig:heradish}
\end{figure*}

@@

%\subsection{Delay spectrum: An estimate of the 21cm power spectrum}
%Add text here. 
 %\textbf{[ Reference to Nithya's foreground simulation work, reference to any plots on the relative contribution of the  foreground and EoR signal. ]}

@@

%need to add in third : Antenna feed focal length 4.5 m which corresponds to a
%signal propagation delay of 0.3 ns. Hence, subsequent reflections from the dish
%vertex are expected to be at a delay which is integral multiple of 0.3 nS.
\begin{figure*}
\centering
\includegraphics[totalheight=0.3\textheight]{plots/frequency_amp_phase_fullbw.png}
\caption{Amplitude and phase of the measured return loss. Colored dashed lines
mark three different frequency bands: $140-160MHz$ (typical power spectrum bandwidth),
$100-200MHz$ (PAPER bandwidth), and
$50-250MHz$ (HERA bandwidth).}
\label{fig:freq}
\end{figure*}
%++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

\begin{figure*}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[width=\linewidth]{plots1/delayspectrum.png}
\caption{Delay transform of the transfer function of the HERA element. The complex return loss of the element is measured between 50 to 400~MHz when the feed is kept at the focal plane of the dish at a focal height 4.5m. The delay spectrum is produced by taking the Fourier transform of the magnitude of the return loss measurement after limiting the measurements between 100 to 200~MHzusing Blackman-Harris window. The intersection of the horizontal and vertical dashed line shows the instrument performance specification as predicted by the theory of delay transform in order to detect the 21cm power spectrum.}
\label{fig:window}
\end{minipage}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[width=\linewidth]{plots1/delayspectrum_feed.png}
\caption{Delay transform of the transfer function of the HERA feed element. The feed is kept on the ground downside up so that the entire radiation from the feed is radiated out. Once again, the measurement is done between 50 to 450 MHz and the delay spectrum is produced between $100-200$~MHz by using a Blackman-Harris window. The black dashed lines illustrate the instrument specification.}
\label{fig:outofthedish}
\end{minipage}
\end{figure*}

@@

The delay response of the instrument is dependent on the band chosen for the Fourier transform.
%As one might expect, in regions where the feed return loss is low, reflections are minimized.  Thus, we cannot ignore that these measurements were performed
%using a PAPER-style feed tuned for efficient operation over a $100-200MHz$ bandwidth. 
The measurement bandwidth effects the amplitude and phase of the delay spectrum. Fourier transforms taken over wider bandwidth
become dominated by the feed sidelobes outside the operating band, making the resultant delay profiles less relevant
for the power spectrum performance of the HERA instrument.  Conversely, when performing Fourier transforms over much 
narrow bands (the windowed $20MHz$ bands typical of PAPER analysis), the width of the resulting delay profile
becomes dominated by sidelobes of low delay emission interacting with the narrow bandwidth kernel.  
Although this may appear to be a relevant performance metric for PAPER power spectrum analysis, such an analysis typically pre-filters out low-delay emission using wide bandwidths precisely to avoid sidelobes from low-delay emission.  Hence, the most relevant delay-spectrum performance profile is that taken using the $100-200MHz$ band. \textbf{In the $100-200MHz$ delay profile, we see a delay response of $-25dB$ at $60ns$, which slopes down to $-60dB$ at $\sim120ns$.  WRITE AGAIN}
\begin{figure}
\centering
\includegraphics[width=\linewidth]{plots1/delayspectrum_height.png}
\caption{Delay transform of the transfer function of the HERA element keeping the feed at various heights. Delay transform is produced by taking the Fourier transform of the measurement using Blackman-Harris window.}
\label{fig:elevator}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{plots/delay_feed.png}
\caption{Delay plots produced using a Hamming window function for different feed only configurations and the PAPER bandwidth ($100MHz-200MHz$). The black dashed lines illustrate our ``60 by 60" specification.}
\label{fig:outofthedish}
\end{figure}

### 2015-12-09 ForegroundSimulations/notes.tex

Figure~\ref{fig:wideband-delay_spectrum} shows the delay spectra of simulated foreground visibilities (in orange) obtained with chromatic (dashed) and achromatic (solid) beams both weighted with the wideband Blackman-Harris window functions in the spectrum, the corresponding CLEAN components in gray and the residuals in black. The depth of deconvolution is set by the limit at which the rms of the residuals inside the horizon limits becomes equal to that on the outside. It is observed that the visibilities simulated with chromatic power pattern (dashed orange) are significantly broadened in delay spectra due to the additional chromaticity. The delay deconvolution is restricted to the {\it foreground wedge} with three additional delay bins on either side of the wedge. Due to this restriction, the residuals inside the horizon delay limits are lower than those outside. Since the simulated visibilities obtained using the achromatic power pattern are predominantly contained well within the horizon delay limits, the delay-domain deconvolution of these delay spectra is much more effective at lowering the residuals (by $\sim 2$ orders of magnitude) than in the case of visibilities obtained with a chromatic power pattern. These delay spectrum residuals correspond to the visibility residuals plotted in Figure~\ref{fig:simulated-visibilities}.

>>>>

Figure~\ref{fig:wideband-delay_spectrum} shows the delay spectra of simulated foreground visibilities (in orange) obtained with chromatic (dashed) and achromatic (solid) beams. Neither of them is weighted with the wideband Blackman-Harris window functions in the spectrum. The corresponding CLEAN components are shown in gray and the residuals in black. The depth of deconvolution is set by the limit at which the rms of the residuals inside the horizon limits becomes equal to that on the outside. It is observed that the visibilities simulated with chromatic power pattern (dashed orange) are significantly broadened in delay spectra due to the additional chromaticity. The delay deconvolution is restricted to the {\it foreground wedge} with three additional delay bins on either side of the wedge. Due to this restriction, the residuals inside the horizon delay limits are lower than those outside. Since the simulated visibilities obtained using the achromatic power pattern are predominantly contained well within the horizon delay limits, the delay-domain deconvolution of these delay spectra is much more effective at lowering the residuals (by $\sim 2$ orders of magnitude) than in the case of visibilities obtained with a chromatic power pattern. These delay spectrum residuals correspond to the visibility residuals plotted in Figure~\ref{fig:simulated-visibilities}.
